Formalizing the Edmonds-Karp Algorithm

### 2016-03-03 paper/root.tex
diagram for benchmark

\pagestyle{plain} % turn on page numbers
\usepackage[utf8]{inputenc}
\usepackage{microtype} % Better typesetting for PDFs -- is enabling this ok?
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{eufrak} %The eufrak package is redundant if the amsfonts package is used
% \usepackage{mathpartir}
%\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\usepackage[boxed]{algorithm}
\usepackage{enumerate}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{color}
\usepackage[noend]{algpseudocode}
\usepackage{caption}
\usepackage[font=scriptsize]{subcaption}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}

\usepackage{multirow}

@@

\section{Benchmarking}
  We have compared the running time of our algorithm against an unverified reference implementation in Java, taken from Sedgewick and Wayne's book on algorithms~\cite{SeWa11}.
  We have done the comparison on randomly generated sparse and dense networks, the sparse networks having a \emph{density} ($\frac{|E|}{|V|(|V| - 1)}$) of $0.02$, and the dense networks having a density of $0.25$. For sparse networks, we varied the number of nodes between $1000$ and $5000$, for dense networks between $1000$ and $1400$.
  The results are shown in Table~\ref{tab:benchmark}. 
  \begin{wrapfigure}{o}{.4\textwidth}
  \vspace{-20pt}
  \begin{center}
  \begin{tabular}{|c|c|c|}
  \hline
  Name        & SML       & Java   \\
  \hline\hline
  1000-sparse & 204       & 15     \\
  2000-sparse & 1430      & 231    \\
  3000-sparse & 4928      & 828    \\
  4000-sparse & 9299      & 2145   \\
  5000-sparse & 23625     & 4868   \\
  1000-dense  & 6575      & 4011   \\
  1100-dense  & 8067      & 5487   \\
  1200-dense  & 10892     & 7011   \\
  1300-dense  & 14070     & 9815   \\
  1400-dense  & 17317     & 12156  \\
  \hline
  \end{tabular}
  \end{center}
  \vspace{-15pt}
  \caption{Dijkstra benchmark}\label{tab:benchmark}
  \vspace{-20pt}
  \end{wrapfigure}

>>>>

\usepackage{etex}
\pagestyle{plain} % turn on page numbers
\usepackage[utf8]{inputenc}
\usepackage{microtype} % Better typesetting for PDFs -- is enabling this ok?
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{eufrak} %The eufrak package is redundant if the amsfonts package is used
% \usepackage{mathpartir}
%\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\usepackage[boxed]{algorithm}
\usepackage{enumerate}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{color}
\usepackage[noend]{algpseudocode}
\usepackage{caption}
\usepackage[font=scriptsize]{subcaption}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{pgfplots}

@@

\section{Benchmarking}
  We have compared the running time of our algorithm against an unverified reference implementation in Java, taken from Sedgewick and Wayne's book on algorithms~\cite{SeWa11}.

\begin{figure}[!h]
\centering    
\begin{tikzpicture}[thick,scale=1, every node/.style={scale=1}] %change the scales if you like to reduce the size
	\begin{axis}[
		%title={Benchmark of the Edmonds-Karp algorithm},
	    axis x line*= bottom,
	    axis y line*= left,
	    xmode = log,
	    ymode = log,
	    xlabel = Number of vertices in the network,
	    ylabel = Execution time in milliseconds,
    	smooth,
	    cycle list name = black white,
	    legend style = { 
	    	at={(0.59,0.4)}, 
    	    anchor=north west,
	        draw=black, 
	        fill= white,
        	align=left
    	}
	]

	%start data for plotting
		\addplot table {
			1000 204
			2000 1430
			3000 4928
			4000 9299
			5000 23625
		}; \addlegendentry{SML, Sparse};

		\addplot table {
			1000 15
			2000 231
			3000 828
			4000 2145
			5000 4868
		}; \addlegendentry{Java, Sparse};

		\addplot table {
			1000 6575
			1100 8067
			1200 10892
			1300 14070
			1400 17317
		}; \addlegendentry{SML, Dense};

		\addplot table {
			1000 4011
			1100 5487
			1200 7011
			1300 9815
			1400 12156
		}; \addlegendentry{Java, Dense};
	%end data for plotting

	\end{axis}
\end{tikzpicture}
%\caption{Edmonds-Karp benchmark}\label{fig:benchmark}
\end{figure}

  We have done the comparison on randomly generated sparse and dense networks, the sparse networks having a \emph{density} ($\frac{|E|}{|V|(|V| - 1)}$) of $0.02$, and the dense networks having a density of $0.25$. For sparse networks, we varied the number of nodes between $1000$ and $5000$, for dense networks between $1000$ and $1400$.
  The results are shown in Table~\ref{tab:benchmark}. 
  \begin{wrapfigure}{o}{.4\textwidth}
  \vspace{-20pt}
  \begin{center}
  \begin{tabular}{|c|c|c|}
  \hline
  Name        & SML       & Java   \\
  \hline\hline
  1000-sparse & 204       & 15     \\
  2000-sparse & 1430      & 231    \\
  3000-sparse & 4928      & 828    \\
  4000-sparse & 9299      & 2145   \\
  5000-sparse & 23625     & 4868   \\
  1000-dense  & 6575      & 4011   \\
  1100-dense  & 8067      & 5487   \\
  1200-dense  & 10892     & 7011   \\
  1300-dense  & 14070     & 9815   \\
  1400-dense  & 17317     & 12156  \\
  \hline
  \end{tabular}
  \end{center}
  \vspace{-15pt}
  \caption{Dijkstra benchmark}\label{tab:benchmark}
  \vspace{-20pt}
  \end{wrapfigure}
